Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify clean_SR

  group_by(
    sequenceID,
    eventID
    ) %>%
  summarize(
    course_current = list(
      unique(item)
      )
    ) %>%

@@

# lhs = course past
d_transcript_cum_current %>%
  filter(!is.na(course_past)) %>%
  unnest(
    course_past,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_past
    ) %>%
  count(
    lhs, 
    rhs
    )

# lhs = course not so far
d_transcript_cum_current %>%
  unnest(
    course_not_so_far,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_not_so_far
    ) %>%
  count(
    lhs, 
    rhs
    )
```

@@

  AR %>%
    filter(
      count >= 5
      ) %>%
    mutate_if(
      is.numeric,
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count,
      confidence, rhs.support,
      lift, 
      everything(),
      - matches("rate|course|grade|outcome|taken")
    ) %>%
    arrange(
      desc(count)
    )

@@

    # Isolate RHS and LHS
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%

    separate(
      rule,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%
    separate(
      lhs,
      into = c("LHS Course ID", "LHS Quality"),
      sep = "_",
      remove= FALSE
      ) %>%
    separate(
      rhs, 
      into = c("RHS Course ID", "RHS Quality"),
      sep = "_", 
      remove = FALSE
    )
}

    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
                             T ~ (support / lhs.rhsCourse.support)),
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = 1 #dummy variable
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support
     ) %>%
    ungroup() %>%
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)

>>>>

  group_by(
    sequenceID,
    eventID
    ) %>%
  summarize(
    course_current = list(
      unique(item_PF)
      )
    ) %>%

@@

# lhs = course past
d_transcript_cum_current %>%
  filter(!is.na(course_past)) %>%
  unnest(
    course_past,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_past
    ) %>%
  count(
    lhs, 
    rhs,
    sort = TRUE
    )

# lhs = course not so far
d_transcript_cum_current %>%
  unnest(
    course_not_so_far,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_not_so_far
    ) %>%
  count(
    lhs, 
    rhs,
    sort = TRUE
    ) %>%
  filter(str_detect(rhs, "fail"))
```

@@

    filter(
      count >= 5
      ) %>%

    mutate_if(
      is.numeric,
      funs(round(., 5))
    ) %>%

    select(
      lhs, rhs,
      support, count,
      confidence, rhs.support,
      lift, 
      everything(),
      - matches("rate|course|grade|outcome|taken")
    ) %>%

    arrange(
      desc(count)
    )

@@

    # Exclude rules with no support
    filter(
      support > 0
      ) %>%

    # separate rule
    mutate(
      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
      ) %>%
    separate(
      rule,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%

    # separate lhs and rhs
    separate(
      lhs,
      into    = c("lhs_course", "lhs_outcome"),
      sep     = "_",
      remove  = FALSE,
      convert = TRUE
      ) %>%
    separate(
      rhs,
      into    = c("rhs_course", "rhs_outcome"),
      sep     = "_",
      remove  = FALSE,
      convert = TRUE
      )

```{r SR metrics}
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
                             T ~ (support / lhs.rhsCourse.support)),
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = 1 #dummy variable
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support
     ) %>%
    ungroup() %>%
```

```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```
